---
title: "Establishing atttiudes towards novel stimuli via the IAT"
subtitle: "Experiment 3"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# dependencies
library(tidyverse)
library(psych)
library(effects)
library(knitr)
library(sjPlot)
library(effsize)
library(lsr)
library(car)
library(plotrix)  # for std.error
library(gridExtra)
library(lme4)
library(patchwork)

# rounds all numerics in a df
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))
  df[,nums] <- round(df[,nums], digits = digits)
  (df)
}
```

# Descriptive statistics

## Full sample

### Age

```{r, message=FALSE, warning=FALSE, echo = FALSE}
# get data
data_df <- read.csv("data/processed/processed data - wide format all tasks.csv")

#data_df <- na.omit(data_df)

#colnames(data_df)

data_df %>% 
  dplyr::select(age) %>%
  psych::describe(fast = TRUE,  # subset of descriptive stats
                  ranges = FALSE,
                  trim = 0) %>%
  dplyr::select(-vars, -se) %>%
  round_df(2) %>%
  kable()
```

### Gender

```{r, message=FALSE, warning=FALSE, echo = FALSE}
data_df %>% 
  dplyr::count(gender) %>%
  kable()
```

## Analytic sample

I.e., after applying inclusion/exclusion criteria.

### Conditions

```{r, message=FALSE, warning=FALSE, echo=FALSE}
passers_df <- 
  data_df %>%
  filter(exclude == FALSE) %>%
  mutate(condition = as.factor(IAT_condition),
         attribute_condition = as.factor(attribute_condition))

passers_df %>% 
  dplyr::count(IAT_condition) %>%
  kable()

passers_df %>% 
  dplyr::count(attribute_condition) %>%
  kable()

passers_df %>% 
  dplyr::count(interaction(IAT_condition, attribute_condition)) %>%
  kable()
```

### Performance on the IAT and SC-IAT

```{r, message=FALSE, warning=FALSE, echo=FALSE}
passers_df %>% 
  dplyr::select(IAT_mean_RT,
                IAT_perc_acc,
                SCIAT_mean_RT,
                SCIAT_perc_acc) %>%
  psych::describe(fast = TRUE,  # subset of descriptive stats
                  ranges = FALSE,
                  trim = 0) %>%
  dplyr::select(-vars, -se) %>%
  rownames_to_column() %>%
  dplyr::mutate(mean = round(mean, 2),
         sd = round(sd, 2)) %>%
  kable()
```

# Outlier removal

RTs <300 ms trimmed. Reciprocal transformation applied. Outliers defined as > 2.5 SD from mean and excluded.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# exclude participants who had more than 10% of trials in less than 300ms, and make variables factors
SCIAT_data <- 
  read.csv("data/processed/processed data - sciat rt data.csv") %>%
  dplyr::rename(SCIAT_block = task) %>%
  dplyr::mutate(participant = as.factor(participant),
                SCIAT_block = as.factor(ifelse(SCIAT_block == "compatibletest_sciat", "Chinese negative", 
                                               ifelse(SCIAT_block == "incompatibletest_sciat", "Chinese positive",
                                                      NA))),
                attribute_condition = as.factor(attribute_condition),
                IAT_condition = as.factor(ifelse(IAT_condition == as.character("Flowers-Chinese IAT"),
                                                 "Flowers",
                                                 ifelse(IAT_condition == as.character("Insects-Chinese IAT"), 
                                                        "Insects", NA)))) %>%
  filter(exclude == FALSE) %>%
  mutate(recip_rt = ifelse(rt >= 300, 1000/rt, NA)) %>%  # trim rts < 300, recip transform to presses per second
  schoRsch::outlier(dv = "recip_rt",  # trim >2.5 SD from mean
                    todo = "elim",
                    upper.z = 2.5,
                    lower.z = -2.5) %>%
  select(-outlier, -zscores)

#sapply(SCIAT_data, class)

ggplot(SCIAT_data, aes(x = recip_rt)) + 
  geom_density() +
  theme_classic()
```

# H1: Differences in SC-IAT effects between IAT contrast category conditions, in the opposite attributes condition

This seeks to replicate the effect found in previous studies. The Chinese characters should acquire the opposite valence to the category they were contrasted with in the IAT (i.e., flowers vs insects).

SCIAT effects are expected to differ between the IAT conditions, where the Chinese characters acquire the opposite valence to the images they were contrasted with in the IAT.

## Linear mixed model

- Hypothesis refers to the IAT_condition*SCIAT_block interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}

# opposite condition only
opp_val_data_only <- SCIAT_data %>%
  filter(attribute_condition == "opposite valenced attributes") 

model_h1 <- lmer(recip_rt ~ SCIAT_block * IAT_condition + (SCIAT_block | participant), 
                contrasts = list(SCIAT_block = "contr.sum", IAT_condition = "contr.sum"),  
                data = opp_val_data_only)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_h1, 
         emph.p = FALSE, 
         p.kr = FALSE,
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_h1, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_h1_predicted_effects <- 
  as.data.frame(effect("SCIAT_block:IAT_condition", model_h1)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
         `SCIAT block` = SCIAT_block)

model_h1_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
ggplot(data = model_h1_predicted_effects,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))
```

# E1: No evidence of differences in SCIAT effects between IAT contrast category conditions, in the non-opposites attributes condition

We expected that when the positive-negative attribute stimuli and category labels were changed to non-words, the evaluative learning effect would disappear.

## Linear mixed model

- Hypothesis refers to the IAT_condition*SCIAT_block interaction effect, which we expect to be non-significant.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
# non-opposite condition only
nonword_val_data_only <- SCIAT_data %>%
  filter(attribute_condition == "nonword attributes")

model_e1 <- lmer(recip_rt ~ SCIAT_block * IAT_condition + (SCIAT_block | participant), 
                contrasts = list(SCIAT_block = "contr.sum", IAT_condition = "contr.sum"),  
                data = nonword_val_data_only)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_e1, 
         emph.p = FALSE,
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_e1, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_e1_predicted_effects <- 
  as.data.frame(effect("SCIAT_block:IAT_condition", model_e1)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
         `SCIAT block` = SCIAT_block)

model_e1_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
ggplot(data = model_e1_predicted_effects,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed (1000/RT)") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))
```

# H2: Evaluative learning effect on the SC-IAT is weakened when the analogy within the IAT is undermined

More specifically, the effect described in H2 should be lower in the non-opposite attributes IAT than the opposite attributes IAT. I.e., the difference between the conditions should itself be significant.

## Linear mixed model

## Model

- Hypothesis refers to the IAT_condition \* SCIAT_block \* attribute_condition interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
model_h2 <- lmer(recip_rt ~ SCIAT_block * IAT_condition * attribute_condition + (SCIAT_block | participant),
                contrasts = list(SCIAT_block = "contr.sum", 
                                 IAT_condition = "contr.sum", 
                                 attribute_condition = "contr.sum"),  
                data = SCIAT_data)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_h2, 
         emph.p = FALSE, 
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_h2, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_h2_predicted_effects <- 
  as.data.frame(effect("SCIAT_block:IAT_condition:attribute_condition", model_h2)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
                `SCIAT block` = SCIAT_block)

model_h2_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}

opp_valenced_condition <- model_h2_predicted_effects %>%
  filter(attribute_condition == "opposite valenced attributes")

p1 <-
  ggplot(data = opp_valenced_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  ggtitle("Opposites IAT condition") +
  ylim(1.61, 1.78) +
  theme(legend.position = "none")
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

nonword_condition <- model_h2_predicted_effects %>%
  filter(attribute_condition == "nonword attributes")

p2 <-
  ggplot(data = nonword_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  ggtitle("Non-opposites IAT condition") +
  ylim(1.61, 1.78) +
  theme(legend.position = c(.8, .8))
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

combined <- grid.arrange(p1, p2, ncol = 2)

#ggsave("combined.pdf")

```

# E2: Evaluative learning effect on the SC-IAT is weakened when the analogy within the IAT is undermined (less conservative model)

Given the marginal effect in the above analysis, we constructed a less conservative exploratory model that removed the random slope for SC-IAT block. This model therefore focused on assessing group differences in the SC-IAT effect and did not attempt to model differences in the SC-IAT effect at the individual level. It provides a less conservative, exploratory test of H2.

## Linear mixed model

## Model

- Hypothesis refers to the IAT_condition \* SCIAT_block \* attribute_condition interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
model_e2 <- lmer(recip_rt ~ SCIAT_block * IAT_condition * attribute_condition + (1 | participant),
                contrasts = list(SCIAT_block = "contr.sum", 
                                 IAT_condition = "contr.sum", 
                                 attribute_condition = "contr.sum"),  
                data = SCIAT_data)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_e2, 
         emph.p = FALSE,
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_e2, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_e2_predicted_effects <- 
  as.data.frame(effect("SCIAT_block:IAT_condition:attribute_condition", model_e2)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
                `SCIAT block` = SCIAT_block)

model_e2_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}

opp_valenced_condition <- model_e2_predicted_effects %>%
  filter(attribute_condition == "opposite valenced attributes")

p1 <-
  ggplot(data = opp_valenced_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  ggtitle("Opposite IAT attributes") +
  ylim(1.61, 1.78) +
  theme(legend.position = "none")
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

nonword_condition <- model_e2_predicted_effects %>%
  filter(attribute_condition == "nonword attributes")

p2 <-
  ggplot(data = nonword_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  ggtitle("Non-opposite IAT attributes") +
  ylim(1.61, 1.78) +
  theme(legend.position = c(.8, .8))
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

#combined <- grid.arrange(p1, p2, ncol = 2)

p1 + p2

# copy and past into a fresh R file to save as 9X4 image
```

# H3: Differences in ratings effects between IAT contrast category conditions, in the opposite attributes condition

This seeks to replicate the effect found in previous studies. The Chinese characters should acquire the opposite valence to the category they were contrasted with in the IAT (i.e., flowers vs insects).

Ratings effects are expected to differ between the IAT conditions, where the Chinese characters acquire the opposite valence to the images they were contrasted with in the IAT.

## Linear mixed model

- Hypothesis refers to the IAT_condition*SCIAT_block interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
# exclude participants who had more than 10% of trials in less than 300ms, and make variables factors
ratings_data <- 
  read.csv("data/processed/processed data - ratings item data.csv") %>%
  dplyr::mutate(participant = as.factor(participant),
                attribute_condition = as.factor(attribute_condition),
                IAT_condition = as.factor(IAT_condition)) %>%
  filter(exclude == FALSE)

#sapply(SCIAT_data, class)

# non-opposite condition only
opp_val_data_only_ratings <- ratings_data %>%
  filter(attribute_condition == "opposite valenced attributes")

model_h3 <- lmer(ratings ~ IAT_condition + (1 | participant), 
                contrasts = list(IAT_condition = "contr.sum"),  
                data = opp_val_data_only_ratings)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_h3, 
         emph.p = FALSE, 
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=1, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_h3, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_h3_predicted_effects <- 
  as.data.frame(effect("IAT_condition", model_h3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

model_h3_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
ggplot(data = model_h3_predicted_effects,
       aes(x = `IAT condition`, y = fit)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  ylab("Rating") +
  xlab("IAT condition") +
  scale_colour_grey() +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))
```

# E3: No evidence of differences in SCIAT effects between IAT contrast category conditions, in the non-opposites attributes condition

We expected that when the positive-negative attribute stimuli and category labels were changed to non-words, the evaluative learning effect would disappear.

Ratings effects are expected to differ between the IAT conditions, where the Chinese characters acquire the opposite valence to the images they were contrasted with in the IAT.

## Linear mixed model

- Hypothesis refers to the IAT_condition*SCIAT_block interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
# exclude participants who had more than 10% of trials in less than 300ms, and make variables factors
ratings_data <- 
  read.csv("data/processed/processed data - ratings item data.csv") %>%
  dplyr::mutate(participant = as.factor(participant),
                attribute_condition = as.factor(attribute_condition),
                IAT_condition = as.factor(IAT_condition)) %>%
  filter(exclude == FALSE)

#sapply(SCIAT_data, class)

# non-opposite condition only
nonword_val_data_only_ratings <- ratings_data %>%
  filter(attribute_condition == "nonword attributes")

model_e3 <- lmer(ratings ~ IAT_condition + (1 | participant), 
                contrasts = list(IAT_condition = "contr.sum"),  
                data = nonword_val_data_only_ratings)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_e3, 
         emph.p = FALSE, 
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=1, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_e3, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_e3_predicted_effects <- 
  as.data.frame(effect("IAT_condition", model_e3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

model_e3_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
ggplot(data = model_e3_predicted_effects,
       aes(x = `IAT condition`, y = fit)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  ylab("Rating") +
  xlab("IAT condition") +
  scale_colour_grey() +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))
```

# H4: Evaluative learning effect on the ratings is weakened when the analogy within the IAT is undermined

More specifically, the effect described in H2 should be lower in the non-opposite attributes IAT than the opposite attributes IAT. I.e., the difference between the conditions should itself be significant.

## Linear mixed model

- Hypothesis refers to the IAT_condition \* SCIAT_block \* attribute_condition interaction effect.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
model_h4 <- lmer(ratings ~ IAT_condition * attribute_condition + (1 | participant), 
                contrasts = list(IAT_condition = "contr.sum", attribute_condition = "contr.sum"),  
                data = ratings_data)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_h4, 
         emph.p = FALSE, 
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=2, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_h4, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_h4_predicted_effects <- 
  as.data.frame(effect("IAT_condition:attribute_condition", model_h4)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

model_h4_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}
ggplot(data = model_h4_predicted_effects,
       aes(x = attribute_condition, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Rating") +
  xlab("IAT condition") +
  scale_colour_grey() +
  theme_classic() 
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))
```


# E4: Impact of IAT block order on SCIAT effects between IAT contrast category conditions

Prompted by reviewer comments, we assessed whether the IAT block order influenced the effect in the condition where we expected to see it.

## Linear mixed model

- Hypothesis refers to the IAT_condition\*iat_block_order\*SCIAT_block interaction effect, which we expect to be non-significant.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
# non-opposite condition only
SCIAT_data <- SCIAT_data %>%
  mutate(iat_block_order = as.factor(ifelse(as.numeric(as.character(participant)) %% 2 == 1, "compatible",
                                            ifelse(as.numeric(as.character(participant)) %% 2 == 0, "incompatible", NA))))

model_e4 <- lmer(recip_rt ~ SCIAT_block * IAT_condition * iat_block_order * attribute_condition + (SCIAT_block | participant), 
                 contrasts = list(SCIAT_block = "contr.sum", 
                                  IAT_condition = "contr.sum", 
                                  iat_block_order = "contr.sum",
                                  attribute_condition = "contr.sum"),  
                 data = SCIAT_data)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_e4, 
         emph.p = FALSE,
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_e4, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_e4_predicted_effects <- 
  as.data.frame(effect("SCIAT_block:IAT_condition:iat_block_order", model_e4)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
                `SCIAT block` = SCIAT_block)

model_e4_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}
compatible_condition <- model_e4_predicted_effects %>%
  filter(iat_block_order == "compatible")

p1 <-
  ggplot(data = compatible_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed (1000/RT)") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  theme(legend.position = "none") +
  ylim(1.55, 1.8) +
  ggtitle("compatible")
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

incompatible_condition <- model_e4_predicted_effects %>%
  filter(iat_block_order == "incompatible")

p2 <-
  ggplot(data = incompatible_condition,
       aes(x = `SCIAT block`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Speed (1000/RT)") +
  xlab("SC-IAT block") +
  scale_colour_grey() +
  theme_classic() + 
  theme(legend.position = c(.3, .8)) +
  ylim(1.55, 1.8) +
  ggtitle("incompatible")
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

grid.arrange(p1, p2, ncol = 2)
```

# E5: Impact of IAT block order on ratings effects between IAT contrast category conditions

Prompted by reviewer comments, we assessed whether the IAT block order influenced the effect in the condition where we expected to see it.

## Linear mixed model

- Hypothesis refers to the IAT_condition\*iat_block_order interaction effect, which we expect to be non-significant.
- Confidence intervals via Wald estimation.

```{r, message=FALSE, warning=FALSE}
# non-opposite condition only
ratings_data <- ratings_data %>%
  mutate(iat_block_order = as.factor(ifelse(as.numeric(as.character(participant)) %% 2 == 1, "compatible",
                                            ifelse(as.numeric(as.character(participant)) %% 2 == 0, "incompatible", NA))))

model_e5 <- lmer(ratings ~ IAT_condition * attribute_condition * iat_block_order + (1 | participant), 
                contrasts = list(IAT_condition = "contr.sum", 
                                 attribute_condition = "contr.sum",
                                 iat_block_order = "contr.sum"),  
                data = ratings_data)
```

## Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sjt.lmer(model_e5, 
         emph.p = FALSE, 
         digits.est = 3,
         digits.ci = 3,
         digits.p = 6,
         p.kr = FALSE,
         show.std = TRUE)
```

## Plot effects

```{r, echo=FALSE, fig.height=2, fig.width=5, message=FALSE, warning=FALSE}
sjp.lmer(model_e5, 
         p.kr = FALSE,
         type = "fe")
```

## Table predictions

```{r, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE}
model_e5_predicted_effects <- 
  as.data.frame(effect("IAT_condition:iat_block_order", model_e5)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

model_e5_predicted_effects %>% 
  round_df(2) %>%
  kable()
```
  
## Plot predictions

```{r, echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}
compatible_condition_ratings <- model_e5_predicted_effects %>%
  filter(iat_block_order == "compatible")

p1 <-
  ggplot(data = compatible_condition_ratings,
       aes(x = `IAT condition`, y = fit)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  ylab("Rating") +
  xlab("IAT condition") +
  ggtitle("compatible") +
  scale_colour_grey() +
  ylim(4.0, 4.7) +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

incompatible_condition_ratings <- model_e5_predicted_effects %>%
  filter(iat_block_order == "incompatible")

p2 <-
  ggplot(data = incompatible_condition_ratings,
       aes(x = `IAT condition`, y = fit)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  ylab("Rating") +
  xlab("IAT condition") +
  ggtitle("incompatible") +
  ylim(4.0, 4.7) +
  scale_colour_grey() +
  theme_classic()
  # theme(legend.justification=c(0.5,1), legend.position=c(0.5,1),
  #       legend.key = element_rect(colour = "transparent"))

grid.arrange(p1, p2, ncol = 2)
```
