---
title: "The IAT as an analogical learning task: Experiment 1"
author: "Ian Hussey"
output: 
  html_notebook:
    highlight: haddock
    toc: yes
  pdf_document: 
    highlight: haddock
    toc: yes
---

Note that R treats the two conditions alphabetically (i.e., Insects, Flowers), so that all effects sizes are retured as negative despite being in line with the hypotheses. All are inverted when reported in the manuscript to make the reported results congruent with the wording of the hypothesis.

```{r, message=FALSE, warning=FALSE}
## Dependencies
library(tidyverse)
library(psych)
library(effsize)
library(lsr)  # for eta sq
library(MBESS)  # for ci.pvaf(), 95% CI on eta2
library(BayesFactor)

## Data acquisition
data_df <- read.csv("/Users/Ian/Dropbox/Work/Manuscripts/Hussey & De Houwer - the IAT as an analogical learning task/Experiment 1/Data/processed data.csv")
```

# Descriptive statistics

Gender counts

```{r}
data_df %>% count(gender)
```

Descriptives for all participants

```{r}
data_df %>% 
  select(age,
         IAT_accuracy,
         IAT_mean_RT) %>%
  psych::describe(fast = TRUE,  # subset of descriptive stats
                  ranges = FALSE,
                  trim = 0)
```

Descriptives by experimental condition

```{r}
data_df %>% 
  select(gender,
         age,
         ratings_pre,
         ratings_post,
         ratings_change_scores,
         D1) %>%
  psych::describeBy(data_df$condition,
                    fast = TRUE,  # subset of descriptive stats
                    ranges = FALSE,
                    trim = 0)
```

# Distribution plots

Ratings change scores

```{r}
ggplot(data = data_df, aes(x = ratings_change_scores, colour = condition, fill = condition)) +
  geom_density(alpha = 0.3) +
  theme_minimal()
```

# Manipulation checks

## Differences in ratings of valenced stimuli

### Frequentist

T test

```{r}
t.test(formula = valenced_stimuli_ratings ~ condition, 
       data = data_df, alternative = "greater")

cohen.d(formula = valenced_stimuli_ratings ~ condition, 
        data = data_df)
```

### Bayes factors

```{r}
ttestBF(formula = valenced_stimuli_ratings ~ condition, 
        nullInterval = c(-Inf,0),
        rscale = "medium",  # i.e., r = .707 # directional hypothesis
        data = data_df)
```

## Differences in (training) IAT effects betwen conditions

### Frequentist

T test

```{r}
t.test(formula = D1 ~ condition, 
       data = data_df, 
       alternative = "less")

cohen.d(formula = D1 ~ condition, 
        data = data_df)
```          

### Bayes factors

```{r}
ttestBF(formula = D1 ~ condition, 
        data = data_df,
        rscale = "medium",  # i.e., r = .707
        nullInterval = c(-Inf,0)) # directional hypothesis
```

# Hypothesis tests

## Differences in ratings changes between conditions

### Frequentist

T test

```{r}
# t test
t.test(ratings_change_scores ~ condition, 
       data = data_df, alternative = "less")  

# effect size
cohen.d(ratings_change_scores ~ condition, 
        data = data_df)
```

Alternative strategy: ANCOVA with pre as covariate

```{r}
model1 <- lm(ratings_post ~ ratings_pre + condition, 
             data = data_df)

ratings_ANCOVA <- 
  etaSquared(model1, 
             type = 3, 
             anova = TRUE) %>% # output full anova results, not just eta2
  as.data.frame()

ratings_ANCOVA

# 90% CI on eta2 
## (nb 90% not 95%, see Wuensch, 2009; Steiger. 2004)
# from http://daniellakens.blogspot.be/2014/06/calculating-confidence-intervals-for.html
# 1. extract individual stats
ancova_F        <-  ratings_ANCOVA$F[2]         # where 2 specifies the main effect row
ancova_df_1     <-  ratings_ANCOVA$df[2]        # where 2 specifies the main effect row
ancova_df_2     <-  ratings_ANCOVA$df[3]        # where 3 specifies the residuals row
ancova_p        <-  ratings_ANCOVA$p[2]         # where 2 specifies the main effect row
ancova_eta2     <-  ratings_ANCOVA$eta.sq[2]    # where 2 specifies the main effect row

n_df <- data_df %>% dplyr::summarize(n_variable = n())
n_integer <- n_df$n_variable

# 2. Use to calculate 90% CIs
ci.pvaf(F.value = ancova_F, 
        df.1 = ancova_df_1, 
        df.2 = ancova_df_2, 
        N = n_integer, 
        conf.level=.90)
```

### Bayes factors

```{r}
ttestBF(formula = ratings_change_scores ~ condition, 
        rscale = "medium",  # i.e., r = .707
        nullInterval = c(-Inf,0), # directional hypothesis
        data = data_df)
```

# Post hoc exploratory tests

Added at the request of our peer reviewers.

### Is the effect influenced by IAT block order? 

Explore interaction effect between condition and block order.

#### Frequentist

```{r}
# check factors are indeed set to factors
sapply(data_df, class)

model2 <- 
  lm(ratings_change_scores ~ condition * block_order, 
     contrasts = list(condition = "contr.sum", block_order = "contr.sum"),  # effect coding for factor variables
     data = data_df)

etaSquared(model2, 
           type = 3, 
           anova = TRUE)
```

#### Bayes factors

```{r}
anovaBF(formula = ratings_change_scores ~ condition * block_order, 
        data = data_df,
        rscaleFixed = "medium",
        multicore = TRUE)
```

