---
title: "Establishing atttiudes towards novel stimuli via the IAT"
subtitle: "Experiment 4"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# dependencies
library(tidyverse)
library(psych)
library(effects)
library(knitr)
library(sjPlot)
library(effsize)
library(lsr)
library(car)
library(plotrix)  # for std.error
library(gridExtra)

# rounds all numerics in a df
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))
  df[,nums] <- round(df[,nums], digits = digits)
  (df)
}
```

# Descriptive statistics

## Full sample

### Age

```{r, message=FALSE, warning=FALSE, echo = FALSE}
# get data
data_df <- 
  read.csv("data/processed/processed data.csv") %>%
  dplyr::mutate(gender = as.factor(gsub("[[:space:]]", "", gender)))

# one missing value found - need to explore why
data_df <- na.omit(data_df)

#colnames(data_df)

data_df %>% 
  dplyr::select(age) %>%
  psych::describe(fast = TRUE,  # subset of descriptive stats
                  ranges = FALSE,
                  trim = 0) %>%
  dplyr::select(-vars, -se) %>%
  kable()
```

### Gender

```{r, message=FALSE, warning=FALSE, echo = FALSE}
data_df %>% 
  dplyr::count(gender) %>%
  kable()
```

## Analytic sample

I.e., after applying inclusion/exclusion criteria.

### Conditions

```{r, message=FALSE, warning=FALSE, echo=FALSE}
passers_df <- 
  data_df %>%
  filter(exclude == FALSE) %>%
  mutate(condition = as.factor(IAT_condition),
         rmts_mastery = as.factor(rmts_mastery))

passers_df %>% 
  dplyr::count(IAT_condition) %>%
  kable()

passers_df %>% 
  dplyr::count(rmts_mastery) %>%
  kable()

passers_df %>% 
  dplyr::count(interaction(IAT_condition, rmts_mastery)) %>%
  kable()
```

### Performance on the IAT and SC-IAT

```{r, message=FALSE, warning=FALSE, echo=FALSE}
passers_df %>% 
  dplyr::select(IAT_mean_RT,
                IAT_perc_acc,
                SCIAT_mean_RT,
                SCIAT_perc_acc) %>%
  psych::describe(fast = TRUE,  # subset of descriptive stats
                  ranges = FALSE,
                  trim = 0) %>%
  dplyr::select(-vars, -se) %>%
  dplyr::mutate(mean = round(mean, 2),
         sd = round(sd, 2)) %>%
  kable()
```

# H1: Differences in SCIAT effects between IAT conditions

SCIAT effects differ between the IAT conditions, where the Chinese characters acquire the opposite valence to the images they were contrasted with in the IAT. This replicates the basic effect found in previous experiments (i.e., evaluative learning via the IAT).

## Hypothesis test

```{r, message=FALSE, warning=FALSE}
attach(passers_df)

t.test(formula = SCIAT_D1 ~ IAT_condition,
       alternative = "two.sided",
       paired = FALSE)

cohen.d(SCIAT_D1 ~ IAT_condition,
        paired = FALSE)
```

Positive *D*1 scores refer to more positive evaluations of the Chinese characters.

# H2: SCIAT effects predicted by the interaction between IAT condition and passing the RMTS

The effect described in H1 is driven by a subgroup of individuals that can analogically relate the stimuli.

## Hypothesis test

Hypothesis refers to the interaction effect.

```{r, message=FALSE, warning=FALSE}
model_2 <- lm(SCIAT_D1 ~ IAT_condition * rmts_mastery,
              contrasts = list(IAT_condition = "contr.sum", rmts_mastery = "contr.sum"),
              data = passers_df)

# anova summary
Anova(model_2, type = 3)

# partial eta squared
model_2 %>%
  etaSquared() %>%
  as.data.frame() %>%
  round_df(3)
```

## Effects table

```{r, message=FALSE, warning=FALSE, echo=FALSE}
sjt.lm(model_2, 
       emph.p = FALSE, 
       show.std = TRUE)
```

## Effects plot

```{r, message=FALSE, fig.height=5, fig.width=7, warning=FALSE, echo=FALSE}
sjp.lm(model_2, 
       type = "fe")
```

## Greyscale inference plot

```{r, cache = TRUE, fig.height=5, fig.width=7}
SCIAT_summary_data <- passers_df %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_SCIAT_D1 = round(mean(SCIAT_D1), 3),
                   se_SCIAT_D1 = round(std.error(SCIAT_D1), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

ggplot(data = SCIAT_summary_data,
       aes(x = rmts_mastery, y = mean_SCIAT_D1, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_SCIAT_D1 + (1.96*se_SCIAT_D1),
                    ymin = mean_SCIAT_D1 + (-1.96*se_SCIAT_D1)),
                position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("SCIAT D1") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() 
```

# Exploratory test 1: H2 is moderated by task order

It is possible that the rmts provided a training context as well as a testing context. The task order might therefore influence the results. This test has been included as a post hoc exploratory test. However, the N per cell is very low, and results should be interpreted with much caution.  

Hypothesis refers to the interaction effect.

```{r, message=FALSE, warning=FALSE}
e_model_1 <- lm(SCIAT_D1 ~ IAT_condition * rmts_mastery * task_order,
              contrasts = list(IAT_condition = "contr.sum", 
                               rmts_mastery = "contr.sum", 
                               task_order = "contr.sum"),
              data = passers_df)

# anova summary
Anova(e_model_1, type = 3)

# partial eta squared
e_model_1 %>%
  etaSquared() %>%
  as.data.frame() %>%
  round_df(3)
```

```{r, cache = TRUE, fig.height=3, fig.width=7}
rmts_first_group <- passers_df %>%
  filter(task_order == "rmts first") %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_SCIAT_D1 = round(mean(SCIAT_D1), 3),
                   se_SCIAT_D1 = round(std.error(SCIAT_D1), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

p1 <- 
  ggplot(data = rmts_first_group,
       aes(x = rmts_mastery, y = mean_SCIAT_D1, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_SCIAT_D1 + (1.96*se_SCIAT_D1),
                    ymin = mean_SCIAT_D1 + (-1.96*se_SCIAT_D1)),
                position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("SCIAT D1") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() +
  coord_cartesian(ylim = c(-.6, .5)) + 
  theme(legend.position = "none")

rmts_second_group <- passers_df %>%
  filter(task_order == "evaluation tasks first") %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_SCIAT_D1 = round(mean(SCIAT_D1), 3),
                   se_SCIAT_D1 = round(std.error(SCIAT_D1), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

p2 <- 
  ggplot(data = rmts_second_group,
       aes(x = rmts_mastery, y = mean_SCIAT_D1, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_SCIAT_D1 + (1.96*se_SCIAT_D1),
                    ymin = mean_SCIAT_D1 + (-1.96*se_SCIAT_D1)),
                position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("SCIAT D1") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() +
  coord_cartesian(ylim = c(-.6, .5)) + 
  theme(legend.position = c(.2, .9))

grid.arrange(p1, p2, ncol = 2)
```

# H3: Differences in ratings between IAT conditions

Ratings differ between the IAT conditions, where the Chinese characters acquire the opposite valence to the images they were contrasted with in the IAT. This replicates the basic effect found in previous experiments (i.e., evaluative learning via the IAT).

## Hypothesis test

```{r, message=FALSE, warning=FALSE}
t.test(formula = mean_rating ~ IAT_condition,
       alternative = "two.sided",
       paired = FALSE)

cohen.d(mean_rating ~ IAT_condition,
        paired = FALSE)
```

Positive ratings refer to more positive evaluations of the Chinese characters.

# H4: Ratings predicted by the interaction between IAT condition and passing the RMTS

The effect described in H3 is driven by a subgroup of individuals that can analogically relate the stimuli.

## Hypothesis test

Hypothesis refers to the interaction effect.

```{r, message=FALSE, warning=FALSE}
model_4 <- lm(mean_rating ~ IAT_condition * rmts_mastery,
              contrasts = list(IAT_condition = "contr.sum", rmts_mastery = "contr.sum"),
              data = passers_df)

# anova summary
Anova(model_4, type = 3)

# partial eta squared
model_4 %>%
  etaSquared() %>%
  as.data.frame() %>%
  round_df(3)
```

## Effects table

```{r, message=FALSE, warning=FALSE, echo=FALSE}
sjt.lm(model_4, 
       emph.p = FALSE, 
       show.std = TRUE)
```

## Effects plot

```{r, message=FALSE, fig.height=5, fig.width=7, warning=FALSE, echo=FALSE}
sjp.lm(model_4, 
       type = "fe")
```

## Greyscale inference plot

```{r, cache = TRUE, fig.height=5, fig.width=7}
ratings_summary_data <- passers_df %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_mean_rating = round(mean(mean_rating), 3),
                   se_mean_rating = round(std.error(mean_rating), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

ggplot(data = ratings_summary_data,
       aes(x = rmts_mastery, y = mean_mean_rating, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_mean_rating + (1.96*se_mean_rating),
                      ymin = mean_mean_rating + (-1.96*se_mean_rating)),
                  position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("Mean ratings") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() 
```

# Exploratory test 2: H4 is moderated by task order

It is possible that the rmts provided a training context as well as a testing context. The task order might therefore influence the results. This test has been included as a post hoc exploratory test. However, the N per cell is very low, and results should be interpreted with much caution.  

Hypothesis refers to the interaction effect.

```{r, message=FALSE, warning=FALSE}
e_model_2 <- lm(mean_rating ~ IAT_condition * rmts_mastery * task_order,
              contrasts = list(IAT_condition = "contr.sum", 
                               rmts_mastery = "contr.sum", 
                               task_order = "contr.sum"),
              data = passers_df)

# anova summary
Anova(e_model_2, type = 3)

# partial eta squared
e_model_2 %>%
  etaSquared() %>%
  as.data.frame() %>%
  round_df(3) %>%
  kable()
```

## Greyscale inference plot

```{r, cache = TRUE, fig.height=3, fig.width=7}
rmts_first_group_ratings <- passers_df %>%
  filter(task_order == "rmts first") %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_mean_rating = round(mean(mean_rating), 3),
                   se_mean_rating = round(std.error(mean_rating), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

p3 <- 
  ggplot(data = rmts_first_group_ratings,
       aes(x = rmts_mastery, y = mean_mean_rating, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_mean_rating + (1.96*se_mean_rating),
                    ymin = mean_mean_rating + (-1.96*se_mean_rating)),
                position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("Mean rating") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() +
  coord_cartesian(ylim = c(2, 7)) +
  theme(legend.position="none")

rmts_second_group_ratings <- passers_df %>%
  filter(task_order == "evaluation tasks first") %>%
  group_by(IAT_condition, rmts_mastery) %>%
  dplyr::summarize(mean_mean_rating = round(mean(mean_rating), 3),
                   se_mean_rating = round(std.error(mean_rating), 3)) %>%
  dplyr::rename(`IAT condition` = IAT_condition)

p4 <- 
  ggplot(data = rmts_second_group_ratings,
       aes(x = rmts_mastery, y = mean_mean_rating, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = mean_mean_rating + (1.96*se_mean_rating),
                    ymin = mean_mean_rating + (-1.96*se_mean_rating)),
                position = position_dodge(width = .1)) +
  # geom_line(aes(group = `IAT condition`),
  #           position = position_dodge(width = .1)) +
  ylab("Mean rating") +
  xlab("RMTS") +
  scale_colour_grey() +
  theme_classic() +
  coord_cartesian(ylim = c(2, 7)) + 
  theme(legend.position = c(.2, .9))

grid.arrange(p3, p4, ncol = 2)
```